Legacy Data Confounds Genomics Studies

### 2018-10-05 legacy.tex
misc

>>>>

\subsection{Frequencies of SNPs in other datasets}
Using the allele frequency files for the Japanese HapMap samples, we extracted the positions we identified as being significantly associated to the average quality of mapped bases. We then compared the frequencies of these 42 SNPs in the 1kGP Japanese samples to those of the HapMap Japanese samples. Figure \ref{HapMap_GnomAD} compares the allele frequencies for suspicious sites that are present in HapMap.

Similarly, using the allele frequencies from GnomAD, we were able to extract 164 sites that are statistically significantly associated to the average quality of mapped bases. However, in this case we compared global allele frequencies in both the 1kGP and GnomAD (Figure \ref{HapMap_GnomAD}).
